Re-analysing the data from @moffatt_inner_2020: A textbook illustration of the absence of evidence fallacy

### 2020-12-16 manuscript.Rmd
minor updates in github readme

# creating a grid of possible sample and effect sizes
parameter_grid <- expand.grid(
  sample_size = seq.int(from = 10, to = 100, length.out = 1e2),
  effect_size = seq.int(from = 0.1, to = 1, length.out = 1e3)
  )

@@

# plotting the results
parameter_grid %>%
  mutate(power = as.numeric(power) ) %>%
  ggplot(aes(x = sample_size, y = effect_size, colour = NULL) ) +
  geom_contour_filled(aes(z = power), alpha = 0.8) +
  # geom_raster(aes(fill = power), interpolate = TRUE) +
  geom_line(
    data = parameter_grid %>% filter(round(power, 3) == 0.9),
    color = "black", lwd = 0.8
    ) +
  geom_segment(
    x = 26, xend = 26, y = 0, yend = target,
    lwd = 0.5, linetype = 3
    ) +
  geom_segment(
    x = 0, xend = 26, y = target, yend = target,
    lwd = 0.5, linetype = 3
    ) +
  geom_point(
    x = 26, y = target,
    pch = 21, size = 3, fill = "white"
    ) +
  theme_bw(base_size = 12) +
  labs(x = "Number of participants (per group)", y = "Standardised mean difference") +
  coord_cartesian(expand = FALSE) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank() ) +
  # scale_fill_manual(values = ., labels = seq(0.304, 2.129, length.out = 10) %>% round(2) )+
  # guides(fill = guide_colorbar() )
  # https://stackoverflow.com/questions/62543112/how-to-make-discrete-gradient-color-bar-with-geom-contour-filled
  # metR::scale_fill_discretised()
  # scale_fill_distiller(super = metR::ScaleDiscretised, palette = "RdYlBu") +
  guides(fill = guide_legend(title = "Power", reverse = TRUE) )
```

>>>>

# creating a grid of possible sample and effect sizes
parameter_grid <- expand.grid(
  sample_size = seq.int(from = 10, to = 100, length.out = 100),
  effect_size = seq.int(from = 0.1, to = 1, length.out = 300)
  )

@@

# plotting the results
parameter_grid %>%
  mutate(power = as.numeric(power) ) %>%
  ggplot(aes(x = sample_size, y = effect_size, colour = NULL) ) +
  geom_contour_filled(aes(z = power), alpha = 0.8) +
  # geom_raster(aes(fill = power), interpolate = TRUE) +
  geom_line(
    data = parameter_grid %>%
      filter(round(power, 2) == 0.9) %>%
      group_by(sample_size) %>%
      summarise(effect_size = mean(effect_size), power = mean(power) ) %>%
      ungroup,
    color = "black", lwd = 0.8
    ) +
  geom_segment(
    x = 26, xend = 26, y = 0, yend = target,
    lwd = 0.5, linetype = 3
    ) +
  geom_segment(
    x = 0, xend = 26, y = target, yend = target,
    lwd = 0.5, linetype = 3
    ) +
  geom_point(
    x = 26, y = target,
    pch = 21, size = 3, fill = "white"
    ) +
  theme_bw(base_size = 12) +
  labs(x = "Number of participants", y = "Standardised mean difference") +
  coord_cartesian(expand = FALSE) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank() ) +
  # scale_fill_manual(values = ., labels = seq(0.304, 2.129, length.out = 10) %>% round(2) )+
  # guides(fill = guide_colorbar() )
  # https://stackoverflow.com/questions/62543112/how-to-make-discrete-gradient-color-bar-with-geom-contour-filled
  # metR::scale_fill_discretised()
  # scale_fill_distiller(super = metR::ScaleDiscretised, palette = "RdYlBu") +
  guides(fill = guide_legend(title = "Power", reverse = TRUE) )
```
